Overlapping Batches for the Assessment of Solution Quality in Stochastic Programs

### 2014-07-08 Referee1_Response.tex

\begin{itemize}
\item[\textbf{M2.}] \textit{The choice of the lower bound that is embedded in equation (8) is interesting. 
(The upper bound in equation (8) is completely natural as the sample mean of the $n_l$ realizations of the function evaluated at $\hat{x}$.) 
It seems that there are also other natural choices that could be made here for the lower bound. 
There is some discussion of this choice in the text that follows equations (7)-(9), but can the authors say more? For example, do the consistency and asymptotic validity results that follow hinge on this choice? Or, do those results also hold for other choices, like forming $\gbb$ as a sample
mean of the underlying $\gb$ values. 
We know that the individual gap estimators in (7) are nonnegative, and if we formed $\gbb$ as a sample mean of $\gb$ values, it would be nonnegative. 
Is the $\gbb$, as specified in (8), nonnegative? 
Have the authors computationally explored other choices here? 
Any insight in this vein would be valuable to the reader in understanding the choice made in equation (8).}
\end{itemize}

\noi
You are right; we did not fully motivate this choice of $\gbb$.  
We added explanations after the definition of the OMRP estimators, motivating this choice and relating it to the theoretical results presented in the paper.\smallskip

\noi 
As you pointed out for the upper bound in (8), this $\gbb$ was chosen for each observation to have equal weight when the sampling problems yield optimal solutions $x_j^* = x^*, \ \forall j$. 
This fact is used in Lemmas 1 and 2, which are then used---directly or indirectly---in proving Theorems 1--3. 
When the alternative $\gbb$, formed as a sample mean of $\gb$ values, is used, 
a subset of the theoretical results can be established (e.g., $\gbb$ converges almost surely to $\mu_{\hat{x}}$). 
However, we had difficulty establishing the same asymptotically lower variances for the new $VG$. 
An alternative is to concurrently adjust the coefficients of the $\dbb$ terms to establish convergence of the new $\gbb$, $VG$, etc.\ to their nonoptimized counterparts $\dbb$, $VD$, etc.
When the coefficients of $\dbb$ are adjusted, however, $\dbb$ and $VD$ are {\it not exactly} the same as the overlapping estimators of simulation output analysis. 
Because our results depend on the asymptotic properties of the overlapping estimators already established in the simulation literature, we did not want to make any changes to $\dbb$. 
It may be still be possible to recover the same results on overlapping using this alternative  $\dbb$ but we did not pursue it here. 
%We actually performed computations using $\gbb$ formed as a sample mean of $\gb$ values and the results were largely similar. 
Due to the lack of theoretical results explained above, we decided not to include or discuss $\gbb$ formed as a sample mean of $\gb$ values, even though it appears as a natural choice. 
Instead, we expanded the text motivating the current choice of $\gbb$. 
Based on your comments, we also expanded the text regarding the nonnegativity of $\gbb$. 
Thank you for your insightful comments. 
\medskip

@@

\begin{itemize}
\item[18.] \textit{p18, l57: The authors speak of coverage probabilities for DB1, but how can this be done without knowing an optimal solution to DB1?}
\end{itemize}

\noindent 
We used a Latin hypercube sample of size 50,000 estimate $\mu_{\hat{x}}$ for DB1, which was then used to estimate the coverage probability of the OMRP confidence intervals for this test problem.
We explain this at the end of Section 5.1 (Test Problems). 
We also changed the wording in Section 5.3 (Results of Experiments) to make it clear that the coverage probability is estimated for DB1. 
\medskip

\begin{itemize}
\item[19.] \textit{p19: It may be possible to expand on the last paragraph of Section 5, in giving guidance on selecting the degree of overlap, depending on the authors' response to comment M1 above.}
\end{itemize}

\noindent 
Based on our study of computational efficiency of the OMRP estimators, we  provided an updated and expanded guidance on selecting the degree of overlap. 
This guidance appears in the last paragraph of \S 5.4 (Computational Efficiency). 
Thank you for this suggestion.

### 2014-07-08 omrp_lb_rev.tex
Referee 1, Major Comment 2

The results on overlapping batch means like (\ref{eq:varvarred}) occur in the limit as $n, m, k=n/m \rightarrow \infty$.  
Let $n_l, m_l$, and $k_l$ be sequences of numbers satisfying these requirements, then the limits will be taken as $l \rightarrow \infty$.  
We assume a batching structure where $m_l = \lfloor n_l ^r \rfloor$ for some $0<r<1$, as is typical in simulation, and $n_l$ tends to infinity as $l \rightarrow \infty$.  
In addition, we may desire that the batch nonoverlap parameter change with $l$, to ensure that $\gamma_l / m_l = \gammab_l$ converges to the constant $\gammab$.  
Now we are ready to define the estimators for OMRP.
\begin{align}
	\gb_{lj} & = \frac{1}{m_l} \sum_{i=1}^{m_l} \left[ f(\xh,\xit^{\gamma_l(j-1)+i}) - f(\xs_j,\xit^{\gamma_l(j-1)+1}) \right],\ \ \ j = 1, 2, \dots, \nbl, \label{eq:gbar} \\
	\gbb_l & = \frac{1}{n_l} \sum_{i=1}^{n_l} \frac{1}{|B(i)|} \sum_{j \in B(i)} \left[ f(\xh,\xiti) - f(\xs_j,\xiti) \right], \label{eq:gbb} \\
	VG_l & = \dfrac{1}{\left( \tfrac{n_l}{m_l} - 1 \right) \left(\nbl\right)} \sum_{j=1}^{\nbl} (\gb_{lj} - \gbb_l)^2. \label{eq:vg}
\end{align}

@@

>>>>

The results on overlapping batch means, discussed in Section \ref{ssec:overlap}, occur in the limit as $n, m, k=n/m \rightarrow \infty$.  
Let $n_l, m_l$, and $k_l$ be sequences of numbers satisfying these requirements, then the limits will be taken as $l \rightarrow \infty$.  
We assume a batching structure where $m_l = \lfloor n_l ^r \rfloor$ for some $0<r<1$, as is typical in simulation, and $n_l$ tends to infinity as $l \rightarrow \infty$.  
In addition, we may desire that the batch nonoverlap parameter change with $l$, to ensure that $\gamma_l / m_l = \gammab_l$ converges to the constant $\gammab$.  
Now we are ready to define the estimators for OMRP.
\begin{align}
	\gb_{lj} & = \frac{1}{m_l} \sum_{i=1}^{m_l} \left[ f(\xh,\xit^{\gamma_l(j-1)+i}) - f(\xs_j,\xit^{\gamma_l(j-1)+1}) \right],\ \ \ j = 1, 2, \dots, \nbl, \label{eq:gbar} \\
	\gbb_l & = \frac{1}{n_l} \sum_{i=1}^{n_l} \frac{1}{|B(i)|} \sum_{j \in B(i)} \left[ f(\xh,\xiti) - f(\xs_j,\xiti) \right], \label{eq:gbb} \\
	VG_l & = \dfrac{1}{\left( \tfrac{n_l}{m_l} - 1 \right) \left(\nbl\right)} \sum_{j=1}^{\nbl} (\gb_{lj} - \gbb_l)^2. \label{eq:vg}
\end{align}

@@

The motivation behind forming $\gbb_l$ by taking into account $B(i)$ is to give each observation $\xit^i$ equal weight. 
This is because we want to be as close to a standard mean estimator (e.g., $\ybb=\frac{1}{n}\sum_{i=1}^{n} y^i$) as possible.
With this definition of $\gbb_l$, when $\xs_j= \xs$ for all $j= 1, 2, \dots, \nbl$, we have $\gbb_l$ equal to its nonoptimized counterpart given in (\ref{eq:dbb}), which is the standard mean estimator. 
This fact is key in establishing the theoretical results presented in the next section. 
We note, however, that this choice of $\gbb_l$ may not be guaranteed to be nonnegative.
In practice, $\max\{\gbb_l,0\}$ can be used as the point estimator of optimality gap to ensure nonnegativity, and $VG_l$ can be calculated the same way given in (\ref{eq:vg}), using $\gbb_l$, to obtain improved interval estimators via overlapping. 
%In our computational results, however, we did not observe any negative values of $\gbb_l$.
